Indirect elicitation as a necessary condition for consistent surrogate losses

### 2020-05-29 neurips-20/cvx-flats.tex
def 8

\begin{definition}[Flat]
	A \emph{flat} $F \subseteq \affhull(\simplex)$ of $\reals^n$ can be written $F=\{x\in\affhull(\simplex) : Wx = \vec 0\}$ for some $W\in\reals^{d\times n}$ where $d\leq n$.
	The codimension of the flat $F$ relative to $\affhull(\simplex)$ is given by $\mathrm{rank}(W)$, and the dimension of $F$ is $n - \mathrm{rank}(W) - 1$.
\end{definition}

>>>>

\begin{definition}[Flat]
	A \emph{flat} $F \subseteq \affhull(\simplex) \subseteq \reals^n$ is a set $F = \ker W \cap \affhull(\simplex)$ for some $W\in\reals^{d\times n}$ where $d\leq n$.
	The codimension of $F$ (relative to $\affhull(\simplex)$) is given by $\codim(F)=\mathrm{rank}(W)$, and the dimension of $F$ is $n - \mathrm{rank}(W) - 1$.
\end{definition}
